### 2017-03-25 thesis/discussion/discussion.tex
finished editing up to the discussion

Since linear models were created only with the ``consistent'' pathway metagene scores, a step wise method was used to generate linear models that included the patient \gls{bmi}, \gls{bmi} status and all of the pathway metagenes that allowed the model to predict the true obesity metagene the best.
As shown by the results in \cref{sec:prediction_of_obesity_associated_metagene_with_pathway_associate_metagene}, all of the models predicted the true obesity metagene scores with high $R^2$-value in Creighton's data set (highest $R^2$ $\approx$ 0.88) and were statistically significant.
This meant that the variables that were significant in the linear models played a role in the obesity associated genetic signatures.
There was no single pathway signature that was common to all of the linear models, but Akt, \gls{egfr} and \gls{pr} pathway metagenes were included in many of the models, which suggested that these pathway signatures may have an important role in the obesity associated genetic signatures (\cref{sub:stepwise_linear_model_prediction_in_nzbc_and_cr_data_sets}).

@@

As shown clearly by the results from \cref{cha:obesity_genetic_signatures_and_cancer}, there seemed to be no  genetic signatures that were able to differntiate between the tumour samples from the patients that were obese from those that were not, across different cancer types.
Furthermore, there were no genes differentially expressed between obese and non-obese patients that were common across multiple cancer types.
These results have suggested that there were no obesity specific genetic signatures that were common across different cancer types.
The results from \cref{cha:obesity_associated_genetic_signature_and_pathway_signatures} showed that the obesity associated genetic signatures generated from the Creighton \textit{et al.} data set were different from those generated from the Fuentes-Mattei \textit{et al.} data set.
None of the pathway associated genetic signatures was similar to any of the obesity associated genetic signatures in the heatmap.
% re-write sentence below:
The results from the linear model prediction suggested a possible association of the obesity associated genetic signatures with the Akt, \gls{egfr} and \gls{pr} pathways.

To summarise, there were no common genetic signatures that significantly associated with the obesity status of the patients.
However, the Akt, \gls{egfr} and \gls{pr} pathways may have a role in promoting the tumour progression in patients that are obese.
Further investigations with good quality data sets and larger patient cohorts are required to clarify the biological relationship between obesity and cancer.

>>>>

Since linear models were created only with the ``consistent'' pathway metagene scores, a step wise method was used to generate linear models that included the patient \gls{bmi}, \gls{bmi} status and all of the pathway metagenes that allowed the model to predict the true obesity metagene the best.
As shown by the results in \cref{sec:prediction_of_obesity_associated_metagene_with_pathway_associate_metagene}, all of the models predicted the true obesity metagene scores with high $R^2$-value in Creighton's data set (highest $R^2$ $\approx$ 0.88) and were statistically significant.
This meant that the variables that were significant in the linear models played a role in the obesity associated genetic signatures.
There was no single pathway signature that was common to all of the linear models, but Akt, \gls{egfr} and Src pathway metagenes were included in many of the models, which suggested that these pathway signatures may have an important role in the obesity associated genetic signatures (\cref{sub:stepwise_linear_model_prediction_in_nzbc_and_cr_data_sets}).

@@

As shown clearly by the results from \cref{cha:obesity_genetic_signatures_and_cancer}, there seemed to be no  genetic signatures that were able to differntiate between the tumour samples from the patients that were obese from those that were not, across different cancer types.
Furthermore, there were no genes differentially expressed between obese and non-obese patients that were common across multiple cancer types.
These results have suggested that there were no obesity specific genetic signatures that were common across different cancer types.
The results from \cref{cha:obesity_associated_genetic_signature_and_pathway_signatures} showed that the obesity associated genetic signatures generated from the Creighton \textit{et al.} data set were different from those generated from the Fuentes-Mattei \textit{et al.} data set.
None of the pathway associated genetic signatures showed positive correlation with any of the obesity associated genetic signatures in the heatmap.
However, strong negative correlation with the Akt, \gls{er}, \gls{egfr}, \gls{pr}, p53, Src and \gls{tgfb} pathways, suggesting that the possibility of the obesity associated genetic signatures were picking up the signals from these pathways, rather than the signals from the obesity phenotype of the patients.
The results from the linear model prediction suggested that the Akt, \gls{egfr} and Src pathways may be important in breast tumour development and/or progression.

To summarise, there were no common genetic signatures that significantly associated with the obesity status of the patients.
However, the Akt, \gls{egfr} and Src pathways may have a role in promoting the tumour progression in patients that are obese.
Further investigations with good quality data sets and larger patient cohorts are required to clarify the biological relationship between obesity and cancer.

### 2017-03-25 thesis/misc/appendix.tex
finished editing up to the discussion

>>>>

	\section{Remainder of the results of the other CR obesity metagenes in the CR data set}
	\label{sec:rest_of_the_cr_ob_meta_heatmap_results_cr}

	All of the other obesity metagenes identified from the CR data set were able to capture the overall gene expressions of the samples in the CR data set (\cref{fig:appendix/cr_ob_meta_heatmap_cr}).
	Furthermore, all of the CR obesity metagenes were significantly associated with the patient \gls{bmi}/\gls{bmi} status in the CR data set (\cref{fig:appendix/cr_ob_meta_box_scatter_cr}).

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=3]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[width=0.32\linewidth,page=8]{appendix/cr_deg_meta_vs_clin}
		\includegraphics[width=0.32\linewidth,page=13]{appendix/cr_deg_meta_vs_clin}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[width=0.32\linewidth,page=23]{appendix/cr_deg_meta_vs_clin}
		\includegraphics[width=0.32\linewidth,page=28]{appendix/cr_deg_meta_vs_clin}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/cr_deg_meta_vs_clin}\\
		\caption[Association of the other CR obesity metagenes with the sample gene expressions in the \gls{nzbc} data]{Heatmaps showing the association of the other obesity metagenes identified from the CR data with the sample gene expressions from the \gls{nzbc} data set.
		Scales are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_heatmap_cris}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=4,width=0.42\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=5,width=0.42\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\caption[Association of the other CR obesity metagenes with the sample \gls{bmi}/\gls{bmi} status in the \gls{nzbc} data]{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{nzbc} data set, respectively.
		P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_cris}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=9,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[page=14,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[page=19,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=24,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[page=29,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\includegraphics[page=34,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/cr_deg_meta_vs_clin}\\
		\caption{Name}
	\end{figure}
